Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-01-24 Report/appendix_tightness.tex
halfcooked

Since the allocated rate of user \me{j} is less than the queued packets, we can find a precoder \me{\mvec{m}{j}} with the additional power of \me{\Delta P} as \me{\mvec{m}{j}^\prime = \bar{\mbf{m}}_{j} + \mvec{V}{j} \mbf{e}^\prime}. Note that the new precoder has no impact on the interference constraint of other users. The newly found precoder \me{\mvec{m}{j}^\prime} minimize the queue of user \me{j} without affecting the rates of other user, there by reduces the objective further. It is in contradiction to our original assumption that the precoders are optimal and the objective is minimum. It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget. Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to minimize the current backlogged packets in the system.

>>>>

Since the allocated rate of user \me{j} is less than the queued packets, we can find a precoder \me{\mvec{m}{j}} with the additional power of \me{\Delta P} as \me{\mvec{m}{j}^\prime = \bar{\mbf{m}}_{j} + \mvec{V}{j} \mbf{e}^\prime}. Note that the new precoder has no impact on the interference constraint of other users. The newly found precoder \me{\mvec{m}{j}^\prime} minimize the queue of user \me{j} without affecting the rates of other user, there by reduces the objective further. It is in contradiction to our original assumption that the precoders are optimal and the objective is minimum.

It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget. Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to minimize the current backlogged packets in the system. The objective of the \ac{JSFRA} problem can be modified to include the power term to find the minimum power precoders as
\begin{equation*}
\| \tilde{\mbf{v}} \|_q + \varphi \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \sum_{n = 1}^{N} \sum_{l=1}^{L} \|\mvec{m}{l,k,n}\|_2,
\end{equation*}
for a small \me{\varphi} which doesn't affect the optimal solution. Note that the above objective is guaranteed to make the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} tight by relaxing the power constraint \eqref{eqn-6.4}.

### 2015-01-24 Report/convergence_centralized.tex
halfcooked

\newcommand{\eqn}[1]{\(#1\)}
\newcommand{\mx}{\mbf{x}}
\newcommand{\my}{\mbf{y}}
\newcommand{\mz}{\mbf{z}}
\newcommand{\mxb}{{\mbf{x}}}
\newcommand{\myb}{{\mbf{y}}}
\newcommand{\iterate}[2]{{#1}^{(#2)}}

@@

Before proceeding further, let us define the following notations. Let \me{\iterate{\mx}{k}} denote the \me{\ith{k}} \ac{AO} operating point and \me{\mx_k} represent the \me{\ith{k}} \ac{SCA} approximation point. Since the problem \eqref{con} is nonconvex, it is not guaranteed to find the optimal solution. In order to solve for a suboptimal solution, let us resort to the \ac{AO} by fixing a block of variables and optimize for others. Since \ac{AO} is an iterative method, let us initialize the variable \me{\my} as \me{\iterate{\myb}{0} \in \mc{F}}. Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is in \ac{DC} form. Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around a feasible point \me{\mxb_0 \in \mc{F}} by

@@

\hat{g}_o(\mx,\iterate{\myb}{0};\mxb_0) = {g}_0(\mxb_0,\iterate{\myb}{0}) + \nabla g_0(\mxb_0,\iterate{\myb}{0})^\mathrm{T} (\mx - \mx_0).

@@

	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mx_k) \leq 0 \eqsub \label{con-dc-m} \\

@@

Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{X}}{i}_{k} \subset \mc{F}}, where \me{\mc{X}} denotes the subset in which \me{\my} is fixed. In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\mx_k}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration. To show that \me{\mx_{k+1}} and \me{\mz_{k+1}} minimizes the objective function ans also feasible, let us assume that the point \me{\mx_k} is feasible for \eqref{con-m}. Since the function \me{{g}_0(\mx,\iterate{\myb}{i})} is linearized around \me{\mx_k}, it satisfies

@@

Thus the sequence \me{f(\mz_k)} is nonincreasing and converges to a critical point. Let \me{\mx_{\ast}} and \me{\mz_{\ast,x,i}} be the optimal point of the problem \eqref{con-m} when the iterative algorithm is converged. The symbol \me{x,i} in \me{\mz_{\ast,x,i}} denotes the optimal \me{\mz} is found over the variable \me{\mx} at the \eqn{\ith{i}} \ac{AO} iteration. Note that this point need not be the stationary point of the original nonconvex problem \eqref{con} since it minimizes over the feasible set \me{\iterate{\mc{X}_{\ast}}{i} \subseteq \iterate{\mc{X}_{\ast}}{i+1} \subset \mc{F}}, which depend on the variable \me{\mx} only. The optimal point \me{\mz_{\ast,x,i}} of the convex subproblem \eqref{con-m} is a stationary point of the nonconvex problem \eqref{con} only over the set \me{\iterate{\mc{X}_{\ast}}{i}}.

Once the optimal solution is found for the fixed \me{\my}, we fix the variable \me{\mx} as \me{\iterate{\mxb}{i} = \mx_{\ast}} and optimize \me{\my}. The problem is still nonconvex due to the \ac{DC} constraint. By following similar approach as earlier, we can obtain an optimal solution \me{\my_{k}} for the convex subproblem at the \me{\ith{k}} iteration. The convergence and the nonincreasing behavior of the problem follows similar explanations. Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,y,i}}. Note that the solution \me{\mz_{\ast,y,i}} is the minimizer for the subset \me{\iterate{\mc{Y}_{\ast}}{i}}

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, \me{f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i+1})}. Let us assume that for an initial feasible value of \eqn{\my} at \eqn{\iterate{\my}{0}}, we achieve a feasible point of \eqref{con} by solving sequence of convex subproblems. The solution is given by \eqn{\mz_{\ast,x,0}} and \eqn{\mx_{\ast}}. Now, by fixing \eqn{\iterate{\mx}{0} = \mx_{\ast}}, we find next feasible solution \eqn{\mz_{\ast,y,0}} and \eqn{\my_{\ast}} for \eqref{con} by solving the convex subproblems \eqref{con-m}. It can be seen that 
\begin{equation}
f_0(\mz_{k,x,0}) \geq f_0(\mz_{\ast,x,0}) \geq f_0(\mz_{0,y,0}) \geq f_0(\mz_{\ast,y,0}),
\end{equation}
which follows from the convexity of the objective function \eqn{f_0} and the initial \eqn{\iterate{\my}{0}} is also a feasible point for the variable \eqn{\my} at the \eqn{\ith{k}} subproblem, \textit{i.e}, 
\begin{equation}
\iterate{\mc{X}}{i}_{0} \dots \subseteq \iterate{\mc{X}}{i}_{\ast} \subseteq \iterate{\mc{Y}_{0}}{i} \dots \subseteq \iterate{\mc{Y}}{i}_{\ast} \subseteq \mc{F}.
\end{equation}
Using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.

>>>>

\newcommand{\eqn}[1]{\(#1\)}
\newcommand{\mx}{\mbf{x}}
\newcommand{\my}{\mbf{y}}
\newcommand{\mz}{\mbf{z}}
\newcommand{\mxb}{{{\mbf{x}}}}
\newcommand{\myb}{{{\mbf{y}}}}
\newcommand{\iterate}[2]{{#1}^{(#2)}}
\newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}

@@

In order to solve the problem, we resort to \ac{AO} by fixing a block of varibles and optimize for others. In the problem \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint in \eqref{con-dc}. In order to solve the problem after fixing the variable \me{\my}, we adopt the \ac{SCA} approach presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets. Since the proposed method involves two level of iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}. Let \me{\iter{\mc{X}}{k}{i}} be a feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and for a fixed \me{\mx}, the set is represented as \me{\iter{\mc{Y}}{k}{i}}. Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denotes the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.

Without affecting the convergence proof, let us consider the variable \me{\my} is fixed in the iteration \me{i} for \ac{AO} and \me{k} for the \ac{SCA} problem to solve for the unique minimizer for \me{\mx \in \iter{\mc{X}}{k}{i}}.

In order to solve for a suboptimal solution, let us resort to the \ac{AO} by fixing a block of variables and optimize for others. Before proceeding further, let us define the following notations. Let \me{\iter{\mx}{k}{i}} denote the \me{\ith{i}} \ac{AO} operating point and \me{k} represent the \me{\ith{k}} \ac{SCA} point. Let us define a set \eqn{\iter{\mc{X}}{k}{i}} as set of feasible values of the subproblem in the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} optimization point for a fixed variable \me{\my}. Since \ac{AO} is an iterative method, let us begin by fixing \me{\my} with the previously found optimal value \me{\iter{\myb}{\ast}{i-1} \in \iter{\mc{Y}}{\ast}{i-1} \subset \mc{F}}, where \me{\ast} in subscript denotes the optimal value over some set \me{\mc{Y}}. Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is in \ac{DC} form. Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1}, the function \me{g_0(\mx,\iter{\myb}{\ast}{i-1})} is linearized around a fixed feasible point \me{\iter{\mxb}{\ast}{i} \in \iter{\mc{X}}{\ast}{i-1} \subset \mc{F}} by

@@

\hat{g}_o(\mx,\iter{\myb}{\ast}{i-1});\iter{\mx}{k}{i})) = {g}_0(\iterate{\mxb}{0},\iterate{\myb}{0}) + \nabla g_0(\iterate{\mxb}{0},\iterate{\myb}{0})^\mathrm{T} (\mx - \iterate{\mxb}{0}).

@@

	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\iterate{\mxb}{k}) \leq 0 \eqsub \label{con-dc-m} \\

@@

Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{X}}{i}_{k} \subset \mc{F}}, where \me{\mc{X}} denotes the subset in which \me{\my} is fixed. In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\iter{\mxb}{k}{i}}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration. To show that \me{\mx_{k+1}} and \me{\mz_{k+1}} minimizes the objective function ans also feasible, let us assume that the point \me{\iterate{\mxb}{k}} is feasible for \eqref{con-m}. Since the function \me{{g}_0(\mx,\iterate{\myb}{i})} is linearized around \me{\iterate{\mxb}{k}}, it satisfies

@@

Thus the sequence \me{f(\mz_k)} is nonincreasing and converges to a critical point. Let \me{\mx_{\ast}} and \me{\mz_{\ast,x,i}} be the optimal point of the problem \eqref{con-m} when the iterative algorithm is converged. The symbol \me{x,i} in \me{\mz_{\ast,x,i}} denotes the optimal \me{\mz} is found over the variable \me{\mx} at the \eqn{\ith{i}} \ac{AO} iteration. Note that this point need not be a stationary point of the problem \eqref{con}, since it is the minimizer only in the feasible set \me{\iterate{\mc{X}_{\ast}}{i} \subset \mc{F}}, which depend on \me{\mx} only.

Once the solution is found for a fixed \me{\my}, we fix \me{\mx} as \me{\iterate{\mxb}{i} = \mx_{\ast}} and optimize for \me{\my}. The problem is still nonconvex due to the \ac{DC} constraint. By following similar approach, we can obtain the minimizer \me{\my_{k}} for the convex subproblem at each iteration \me{{k}}. The convergence and the nonincreasing behavior of the problem follows similar arguments as above. Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,y,i}}. Note that the solution \me{\mz_{\ast,y,i}} is the minimizer in the subset \me{\iterate{\mc{Y}_{\ast}}{i}}.

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, \me{f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i+1})}. Let us consider the \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} is obtained as \eqn{\mx^{(i)}_{\ast}} and \eqn{\mz_{\ast,x,i}} using a fixed \eqn{\my} as \eqn{\my_{\ast}^{(i-1)}}. In order to find \eqn{\iter{\my}{\ast}{i}}, we fix \eqn{\mx} as \eqn{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since the problem \eqref{con} is nonconvex even after fixing \me{\mx}, we have to linearize the convex function in the \ac{DC} constraint \eqref{con-dc} around some fixed operating point of \me{\my}. Since the linearization is performed with the earlier optimal point \eqn{\iter{\my}{\ast}{i-1}}, the feasible set now includes \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\} \in \mc{Y}^{(i)}_{0}}. Now the optimization is performed to find the optimal \me{\my} using the relaxed problem \eqref{con-m}, the optimal solution \me{\mz_{0,y,i}} for the initial iteration after \ac{AO} update follows \me{f_0(\mz_{0,y,i}) \leq f_0(\mz_{\ast,x,i})}, since the feasible set includes the earlier optimal points \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\}}. Note that it is not possible to say \me{\iter{\mc{X}}{\ast}{i} \subseteq \iter{\mc{Y}}{0}{i}} since the set is nonconvex on \me{\mx,\my}, but \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}. Now by using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.
